\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{amsmath}

% moderncv themes
\moderncvstyle{banking}
\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{rgb}{0,0.2,0.9}% red
\definecolor{color2}{rgb}{0.0,0.0,0.0}% dark grey

\usepackage[scale=0.71]{geometry}

% personal data
\firstname{Bowen}
\familyname{Peng}
\address{University of Electronic Science and Technology of China}{No.2006, Xiyuan Ave, West Hi-Tech Zone, Chengdu, Sichuan, P.R.China}{Zip code: 611731}
\mobile{+86~158~8216~6726}
\email{salvare219w@gmail.com}


\begin{document}

\makecvtitle

\section{Basic Info}
\cvitem{Name}{Peng Bowen}
\cvitem{Age}{24(1993-3-13)}
\cvitem{Graduation time}{2018-6}

\section{Education}
\cventry{2015--now}{Postgraduate of Communication and Information Engineering}{University of Electronic Science and Technology of China}{}{}{    
    \begin{itemize}
        \item got scholarship when Grade 1, and two thesis on GlobalCom as the Second author
    \end{itemize}
}

\cventry{2011--2015}{Bachelor of Communication and Information Engineering}{University of Electronic Science and Technology of China}{}{}{
    \begin{itemize}
        \item every year got scholarship, the member of school ACM team, and was recommended for admission to be a master
    \end{itemize}
}

\section{Experience}
\subsection{Scientific Research}
\cventry{2015--now}{Postgraduate}{\textsf{Communication and Information Engineering}}{}{}{
    \begin{itemize}
        \item My major research area is the traffic engineering and rules placement in SDN(Software Define Network). 
        \item Assist several Ph.D with their thesis, coding the main program they need, and discuss the result with them.
    \end{itemize}
}

\subsection{Internship}
\cventry{2017.6--now}{AILab-cv Trainee}{\textsf{Bytedance Inc.}}{}{}{
    \begin{itemize}
        \item Speed up deep learning frame on Android. 
        \item learn about deep learning code implementation, and speed up based on ARM CPU order set to optimize each layer.
    \end{itemize}
}


\subsection{Miscellaneous}
\cventry{2013--2015}{Team member}{UESTC ACM-ICPC Team}{}{}{
    \begin{itemize}
        \item Learning numerous algorithms and data structures, particularly in computing geometry, graph theory and dynamic programming.
        \item Have account on famous coding website, CodeForce(ID:Nanaya)rating 2201, rank 535 of 33750(2017.3), TopCoder(ID:rulez123)rating 2026.
        \item Enter quarter-final in many programming contest, such as GCJ ,TCO and BOP, every year.
    \end{itemize}
}
\cventry{2014}{Judge and problem setter}{2014 Sichuan Provincial Collegiate Programming Contest}{}{}{
    \begin{itemize}
        \item set 4 of 10 problems independently, and help with other 6 problems. 
        \item During the match, judge problem and answer necessary questions.
    \end{itemize}
}


\section{Awards}
\subsection{ACM-ICPC}
\cventry{2015}{The ACM-ICPC Asia Regional Contest Shanghai Site 2015 invitational tournament}{Silver Medal}{}{}{}
\cventry{2014}{The ACM-ICPC Asia Regional Contest Beijing Site 2014}{Gold Medal}{}{}{}
\cventry{2014}{The ACM-ICPC Asia Regional Contest Guangzhou Site 2014}{Silver Medal}{}{}{}
\cventry{2014}{The ACM-ICPC Asia Regional Contest Shanghai Site 2014 invitational tournament}{Gold Medal}{}{}{}
\cventry{2014}{The ACM-ICPC Asia Regional Contest Xi'an Site 2014 invitational tournament}{Gold Medal}{}{}{}
\cventry{2013}{The ACM-ICPC Asia Regional Contest Hangzhou Site 2013}{Silver Medal}{}{}{}

\subsection{Programming Contest}
\cventry{2016}{10th IEEEXTREAM programming contest}{Global rank 7}{}{}{}
\cventry{2016}{14th UESTC school Programming Contest}{1st place}{}{}{}
\cventry{2015}{7th Sichuan Provincial Collegiate Programming Contest}{2nd place}{}{}{}
\cventry{2014}{2014 Southwest Jiaotong University Programming Contest}{1st place}{}{}{}
\cventry{2014}{2014 Sichuan University Programming Contest}{2nd place}{}{}{}



\section{Skill}
\subsection{Languages skills}
\cvitemwithcomment{English}{CET band 6}{passed}

\subsection{Programming skills}
\cvitem{Languages}{C, C++, Python, C\#, Matlab}
\cvitem{Reverse Engineering}{NET.Reflector, IDA}
\cvitem{Revision control}{Git}
\cvitem{Game Engine}{Unity}
\cvitem{Others}{\LaTeX}


\end{document}